---
title: "Assignment 1"
author: "Christopher and Lisa"
date: "2. October 2015"
output: 
  ioslides_presentation:
    logo: logo.png
---

```{r echo=FALSE, include=FALSE}
try(setwd("C:/Users/Christopher/Google Drive/Collaborative Data Analysis/CollaborativeDataAnalysisChristopherAndLisa/Assignment_1/"), silent = TRUE)
try(setwd("C:/Users/Lisa/Documents/GitHub/CollaborativeDataAnalysisChristopherAndLisa/Assignment_1"),silent=TRUE)
source("RCode1_Assignment1.R")
source("RCode2_Assignment1.R")
```

## Introduction

This is an R Markdown presentation by Christopher and Lisa. It presents the results of the analyses run as part of Assignment 1.

The data used for the analysis is (1) the preinstalled "*WWWusage*" and (2) the "*HairEyeColor*" data. The first one is a time series of the numbers of users connected to the Internet through a server every minute. The second one is a cross-sectional data set describing the hair and eye color as well as sex of 592 statistics students. 

Let's start with the first one.

## WWWusage: Line Chart
This is a line chart of the time series data. The number of users is lowest (`r WWWusage.min`) in the beginning, increases at the 10th minute and has three spikes until it decreases again at minute 55. Another increase happens at minute 78, until the number of users reaches its peak, which is `r WWWusage.max` users.
```{r echo=FALSE, error=FALSE}
plot(type ="l", WWWusage, main="Number of users connected to the Internet 
  through a server every minute", 
  lwd=2, col="blue", ylab="Number of users",xlab="Time in minutes")
```

## WWWusage: Mean

The mean of the time series is `r mean(WWWusage)`. Let's plot this together with the time series.

```{r echo = FALSE, error = FALSE} 
plot(type ="l", WWWusage.mean, main="Number of users connected to the Internet 
  through a server every minute", 
  lwd=2, col="blue", ylab="Number of users",xlab="Time in minutes")
lines(data$time, data$WWWusage, col="green")
```

## WWWusage: Log

Now let's plot the difference in log of the time series to get the percentage change. The time series now seems to be very close to stationary data.

```{r echo = FALSE, error = FALSE} 
plot(type = "l", WWWusage.log.diff, main="Difference in number of users connected to the Internet 
     through a server every minute", 
     lwd=2, col="blue", ylab="Difference",xlab="Time in minutes")
```

## WWWusage: Rescaling

Now we plot specific parts of the time series which allows for rescaling, in this case the first 10 observations
```{r echo = FALSE, error = FALSE}
plot(WWWusage[1:10], type="l", main="Number of users connected to the Internet 
  through a server every minute, first 10 observations", 
  lwd=2, col="blue", ylab="Difference",xlab="Time in minutes")
```

## HairEyeColor: Descriptives
Our second data set is the preinstalled "*HairEyeColor*" data.

The data set includes the variables "Hair, "Eye", "Sex" and "Freq". It has `r NCOL(HairEyeColorData)` variables and `r NROW(HairEyeColorData$Hair)` observations, although the sum of individuals included in the data set is `r sum(x)`.

After summing up all individuals with the same eye and hair color, we get the following distribution:

```{r echo = FALSE, error = FALSE}
print(x)
```

## HairEyeColor: Visualization

In order to check for a relationship between hair and eye color, we can look at a mosaicplot of the data.

```{r echo = FALSE, error = FALSE}
fill_colors <- colors()[c(56,130,146,230)]
fill_colors[4] <- "#6ca580"
y <- x[c(3,1,2,4),]
mosaicplot(y, main = "Relationship between hair and eye color", 
           color=fill_colors)
```
