---
title: "R-File 1 for Assignment 1"
author: "Christopher"
date: "25. September 2015"
output: ioslides_presentation
---

```{r echo=FALSE, include=FALSE}
setwd("C:/Users/Christopher/Google Drive/Collaborative Data Analysis/CollaborativeDataAnalysisChristopherAndLisa/Assignment_1/")
source("RCode1_Assignment1.R")
source("RCode2_Assignment1.R")
```

## Introduction

This is an R Markdown presentation by Christopher. It presents the results from Analysis 1 for Assignemnt 1.

The data used for the analysis is the WWWusage data.A time series of the numbers of users connected to the Internet through a server every minute.

## Line Chart

```{r echo=FALSE}
plot(type ="l", WWWusage, main="Number of users connected to the Internet 
  through a sever every minute", 
  lwd=2, col="blue", ylab="Number of users",xlab="Time in minutes")
```

## Slide with R Code and Output

```{r}
mean(WWWusage.first10)
```

## Slide with Plot


## Dataset 1: Hair and Eye Color
For the first assignment we want to analyze the preinstalled R dataset "*HairEyeColor*".
Before getting started, we should set the working directory and load the data set.

For exploring the dataset, we should familiarize ourselves with it. The data set has `r NCOL(HairEyeColor_dataframe)` variables and `r NROW(HairEyeColor_dataframe$Hair)` observations. It includes the following variables: `r print(1,)

```{r, echo=FALSE}
summary("HairEyeColor_dataframe")
```

